The Galactic Midplane is Not a Plane: Implications for {\em Gaia}

### 2019-04-16 paper/ms.tex
Fix Jr error calc

\newcommand{\abs}[1]{\left| #1 \right|}
\newcommand{\z}{z_r}
\newcommand{\uth}{\textsuperscript{th}}
\newcommand{\n}{\text{n}}

@@

An induced error in $z$ of $\Delta z$ will cause $\Delta A_z \sim \Delta z$.
Similarly, an induced error in $R$ will cause $\Delta A_R \sim \Delta R$. If
we assume that $\kappa$ and $\nu$ are constant (\Gus{justify?}), then we have
that
\beq\label{eq:actions_epi_error}
\begin{split}
\Delta L_z = \Delta R v_c &\implies \frac{\Delta L_z}{L_z} = \frac{\Delta R}{R} \\
\Delta J_r = 2 \kappa \Delta A_R &\implies \frac{\Delta J_r}{J_r} = \frac{2\Delta R}{A_R} \\
\Delta J_z = 2 \nu \Delta A_z &\implies \frac{\Delta J_z}{J_z} = \frac{2\Delta z}{A_z}\text{.}
\end{split}
\eeq
Therefore, errors in each action are linearly proportional to the errors in
either the midplane or cylindrical radius. We will check these formulae
against numerical tests next.

>>>>

\newcommand{\abs}[1]{\left| #1 \right|}
\newcommand{\avg}[1]{\left< #1 \right>}
\newcommand{\z}{z_r}
\newcommand{\uth}{\textsuperscript{th}}
\newcommand{\n}{\text{n}}

@@

An induced error in $z$ of $\Delta z$ will cause $\Delta A_z \sim \Delta z$.
Similarly, an induced error in $R$ will cause $\Delta A_R \sim \Delta R$. If
we assume that $\kappa$ and $\nu$ are constant (\Gus{justify?}), then we have
that
\beq\label{eq:actions_epi_error}
\begin{split}
\Delta L_z = \Delta R v_c &\implies \frac{\Delta L_z}{L_z} = \frac{\Delta R}{R} \\
\Delta J_r = 2 \kappa \Delta A_R &\implies \frac{\Delta J_r}{J_r} = \frac{2\Delta R}{A_R} \\
\Delta J_z = 2 \nu \Delta A_z &\implies \frac{\Delta J_z}{J_z} = \frac{2\Delta z}{A_z}\text{.}
\end{split}
\eeq
Therefore, errors in each action are linearly proportional to the errors in
either the midplane or cylindrical radius.

There is a slight complication in the formula for computing $\Delta J_r/J_r$.
In a moment we will consider the effect of an inaccuracy in the distance from
the Sun to the Galactic center on actions. However, this inaccuracy induces an
error in $x$, or $\Delta x$. This is not the same as an inaccuracy in $\Delta
R$, but they are related by the following argument. An error $\Delta x$ will
induce an erroneous radius $R_{\text{err}}$ related by the formula,
\beq
(x+\Delta x)^2 + y^2 = R_{\text{err}}^2\text{.}
\eeq
Keeping only terms to first order in $\Delta x$, we have that,
\beq
\begin{split}
R_{\text{err}}^2 &= R^2 - 2 R \cos{\theta} \Delta x \\
\implies \Delta R &\equiv \abs{R_{\text{err}} - R} = \abs{\cos{\theta}} \Delta x\text{.}
\end{split}
\eeq
Averaging over the circle, we therefore have that
\beq
\avg{\Delta R} = \frac{2}{\pi} \Delta x\text{.}
\eeq
Therefore, the error in $J_r$ is related to $\Delta x$ by,
\beq\label{eq:Jr_epi_dx}
\frac{\Delta J_r}{J_r} = \frac{4 \Delta x}{\pi A_R}\text{.}
\eeq

We will check these formulae against numerical tests next.
